Effects of CHILDREN's programs

### 2020-02-21 paper.tex
removed standardized variables from double selection analysis
added examples in LaTeX file

@@

\section{Outline}
Descriptive statistics\\
- dynamics of selected outcomes\\
- dynamics of real subsidy per institution\\
- dynamics of real total subsidy\\
- dynamics of real subsidy per individual\\

@@

Outlook for CHILDREN\\
- partition analysis\\
(- correlation matrix)\\
(- factor analysis)\\
- general tips\\

>>>>

% working with knitR and LaTeX
% https://kbroman.org/knitr_knutshell/pages/latex.html
% Command line
% R -e 'library(knitr);knit("knitr_example.Rnw")'

@@

\section{Outline}
Descriptive statistics\\
- dynamics of selected outcomes\\
- dynamics of real subsidy per institution\\
- dynamics of real total subsidy\\
- dynamics of real subsidy per individual\\
(- which variables have largest variance; also relevant for variable selection)\\

@@

Outlook for CHILDREN/variable selection\\
- double selection \\
- partition analysis\\
(- correlation matrix)\\
(- factor analysis)\\
- general tips\\

Examples\\

Equation\\

\begin{equation}
\label{ModelProdu}
\ln y_{it} = \beta_0 + \beta_k \ln k_{it-1} + \beta_n \ln n_{it} + \beta_m \ln m_{it} + \beta_t D_t + \beta_i D_i + \epsilon_{it}
\end{equation}

List\\

\begin{itemize}
  \item{The firm is not incorporated in the U.S. (FIC is not equal to USA.)}
  \item{The company is from the financial or utilities sector. This is the case when the SIC code lies between 4900 and 4999 or between 6000 and 6999.}
  \item{A firm's acquisitions are larger than five percent of the value of its total assets. This is the case when AQC over AT is larger than 0.05.} 
\end{itemize}

Figure

\begin{figure}
  \caption{Dispersion in productivity levels}
  \label{LineDisp}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}

{\centering \includegraphics[width=0.8\textwidth]{ANALYSIS/GRAPHS/unnamed-chunk-2-1}

}

\end{knitrout}
\floatfoot{Note: Time series plots of approximate deviations of the three annual dispersion measures from their trends in percent. A shows the full sample, B the non-durable manufacturing sector, and C the durable manufacturing sector. After taking the natural logarithm of the dispersion measures defined in equation 1, I have isolated their cyclical components with an HP-100 filter. The shaded bars represent recessions as defined by the NBER. The year ticks refer to January 1. The dispersion measures take as their date the middle of the year, July 2. Compare Kehrig (2015), Figure 1.}
\end{figure}
